This section investigates the output of speaker recognition systems when
features computed from fake data generated with WaveNet and sampleRNN is used as
input. As described in \ref{sub:speaker_recognition}, we train a speaker
recognition systems with several speakers, including the speakers used to train
WaveNet and sampleRNN. 

\subsection{WaveNet} % (fold)
\label{sub:res-WaveNet}
We attempted to replicate the model described in~\cite{van2016wavenet} but,
unfortunately, we do not have access to Google's computing power nor to the
North American Speech dataset Google used to train the WaveNet model that
produced the samples referenced in \cite{van2016wavenet}. Nonetheless, we used
the data from CSTR VCTK to train speaker dependent WaveNet speech synthesis
models that converged to producing speech that resembled the speakers voice but
sounded like babbling. None of the WaveNet samples produced with our model were
successful in targeted or untargetted attacks to the speaker recognition
system~\footnote{Neither was it successful attacking a GMM-UBM speaker
recognizer.\label{foot:gmm_ubm}.}
% subsection WaveNet (end)
\subsection{sampleRNN} % (fold)
\label{sub:samplernn}
We also tested samples from sampleRNN \cite{mehri2016samplernn}, another
autoregressive architecture that has been successfully used to generate both
speech and music samples. SampleRNN uses a hierarchical structure of deep RNNs
to model dependencies in the sample sequence. Each deep RNN operates at a
different temporal resolution so as to model both long term and short term
dependencies. We generated samples from the three-tiered variant, trained on the
Blizzard 2013 dataset \cite{prahallad2013blizzard}, a 300 hour corpus of a
single female speaker's narration. We also downloaded 10 second samples from the
original paper's online repository at
\texttt{https://soundcloud.com/samplernn/sets}, which we qualitatively found to
have less noise than our generated ones. None of the sampleRNN samples produced
with our model nor with the model produced by~\cite{mehri2016samplernn} were
successful in targeted or untargetted attacks to the speaker recognition
system.~\ref{foot:gmm_ubm}
% subsection SampleRNN (end)
